% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode
% !TEX spellcheck = en_US
% !BIB TS-program = natbib
% Written by Dylan Gatlin (dgatlin5@gmail.com)
\documentclass[defaultstyle,11pt]{apsthesis}

\usepackage{amssymb}		% to get all AMS symbols
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage[authoryear, sort]{natbib} % For citations
\usepackage[yyyymmdd]{datetime} % For YYYY-MM-DD dates
\usepackage{todonotes}      % In case you want to work on something later
\usepackage[nice]{nicefrac} % For inline fractions
\usepackage{multicol}       % For twocolumn equations
\usepackage{multirow}       % For complicated tables
\usepackage{amsmath}        % For calculus notation like partials and derivatives
\usepackage{commath}        % Companion to amsmath
\usepackage{textcomp}
\usepackage{siunitx}        % Proper unit notation
\input macros.tex           % For defining common symbols

%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Methods to Detect Habitable Atmospheres on the Terrestrial Exoplanet TRAPPIST-1 e}

\author{D.}{Gatlin}



\degree{Bachelors in Arts}		%  #1 {long descr.}
	{B.A., Astrophysics}		%  #2 {short descr.}
\dept{Department of}			%  #1 {designation}
	{Astrophysical and Planetary Science}		%  #2 {name}

\advisor{Dr.}				%  #1 {title}
	{Eric T. Wolf}			%  #2 {name}
\advisordept{Atmospheric and Oceanic Sciences}
\reader{Prof. Ann-Marie Madigan}		%  2nd person to sign thesis
\readerdept{Astrophysical and Planetary Sciences}
\readerThree{Prof. David Brain}  % 3rd person to sign thesis
\readerThreedept{Astrophysical and Planetary Sciences}
\readerFour{Prof. Daniel Jones}
\readerFourdept{Arts and Sciences Honors Program}

\defenseDate{\formatdate{3}{5}{2019}} % (m)m (d)d yyyy

\abstract{In order to better direct future exoplanetary research, we must be
 able to accurately predict what telescopes like the James Webb Space Telescope
 (JWST)
 will be able to detect. To this effect, NASA's Planetary Spectrum Generator
 (PSG) can be used to simulate observations, both during exoplanet transits and
 throughout an exoplanet's year. Such predictions allow us to make informed
 decisions about how to spend time on JWST and which techniques will allow for
 different types of analysis. In order to produce the most realistic results from
 the Planetary Spectrum Generator (PSG), self-consistent three-dimensional climate
 models of planets in the TRAPPIST-1 system are first used to simulate
 atmospheres on these tidally locked exoplanets, and understand how they might
 be different from the climate of Earth.

The TRAPPIST-1 exoplanets are assumed to be tidally locked with the host star.
 Recent climate modeling studies indicate that there are three distinct types of
 tidally locked exoplanet atmospheres; slow rotators, fast rotators, and an
 intermediate regime. Slow rotators have large substellar clouds that remain
 constant over time. Fast rotators will have a significant Coriolis force,
 resulting in much smaller substellar clouds and more intense zonal
 winds which advect clouds to the eastern side of the substellar point. In all
 cases, the thermal emission of a planet depends strongly on the spatial
 distribution of clouds, which would change from the perspective of a distant
 observer over the exoplanet's year.

I have constructed a data pipeline that uses climate models as inputs, then
 uses the PSG to produce spectra. This pipeline can use a number of
 climate models on a number of different planets to create
 transit spectra or thermal phase curves.

When studying terrestrial exoplanets, the most exiting cases are potentially
 habitable
 planets. The TRAPPIST-1 system is one of the most likely systems to host a 
 habitable exoplanet. TRAPPIST-1 e is the most likely habitable planet in the
 system. The most effective methods for JWST are the transit method and thermal
 phase curves. The transit method is the most widely used method for detecting
 exoplanets, and JWST will have high resolution spectrographs that will be able
 to detect many atmospheric species including \chem{CO_2} and \chem{H_2O}.
 Additionally, accurate spectra may enable us to infer the
 surface temperature of a planet.

Transit spectra can tell us a lot about the terminator profile of an atmosphere,
 but it cannot tell us about other parts of the planet's surface. Transit
 spectra can also be prone to extinction by clouds or aerosols. Thermal phase
 curves will observe how the thermal emission of an exoplanet will change
 over the course of its year, and may be able to detect features like the nature
 of the substellar cloud, if a planet has entered a runaway greenhouse effect,
 or a snowball state. Thermal phase curves will look dramatically different for
 fast rotators like TRAPPIST-1 e compared to slow rotators, and these results
 can only be simulated with global circulation models used in conjunction with
 accurate radiative transfer models. Thermal phase curves are also very
 sensitive to the planet's temperature, and can therefore help determine if a
 planet is habitable. Future predictions for JWST should
 incorporate the results from global circulation models, and those models should
 be accurate to the exoplanets in question. Future observations should also
 consider thermal phase curves because they will be able to detect a range of
 different
 features than transit spectra and will enable us to more effectively understand
 potentially habitable terrestrial exoplanets.
}

\dedication[Dedication]{	% NEVER use \OnePageChapter here.
    \begin{center}To my Grandpa, Dr. Terry Flanagan\\
    1938 -- 2018
    \end{center}
}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
Thank you to my family who helped encourage me on my way to becoming an
 astrophysicist. To my dad, my mom, and my sister, Mark, Erin, and Carolyn
 Gatlin. To my girlfriend, Grace Marshall.

Thank you to my advisors, Susan (Astromom) Armstrong and David Brain.
 To the professors I've worked alongside, Prof. Jeremy Darling and
 Prof. Seth Hornstein. To
 my research advisors, Prof. Guy Stringfellow and Dr. Eric Wolf.

Thank you to everyone who read my drafts, Prof. Donald Wilkerson and all my peers
 in PHYS 3050.

Thank you to my professors Prof. Zach Berta-Thompson, Prof. Nick Schneider,
 Prof. John Bally,
 Dr. Mathis Habich, Prof. Melissa Nigro, Prof. Jen Kay, Prof. Peter Pilewskie,
 and Prof. Alexandra Jahn. To my high school math teacher, Laurie Buchanan.

Thank you to my co-investigators, Dr. Eric Wolf, Dr. Ravi Kopparapu,
Dr. Geronimo Villanueva, and Dr. Avi Mandell.

\facilities{Exoplanet Archive, Planetary Spectrum Generator}}

% \IRBprotocol{E927F29.001X}	% optional!

\ToCisShort	% use this only for 1-page Table of Contents

\LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

\LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\input ./intro/introduction.tex
\input ./background/background.tex
\input ./models/models.tex
\input ./methods/methods.tex
\input ./spectra/spectra.tex
\input ./tpc/thermal_phase_curves.tex
\input ./conclusion/conclusion.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{aasjournal}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{thesis_citations}		% Bib database in "refs.bib"

%%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input appendix.tex

\end{document}

